\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Say where B1 skips ahead to (P1).
Minor edits through background and methodology.

Bridges are unlisted alternative entry nodes used to connect to Tor when Tor relays are censored.
Bridges also receive packets from the user and forward traffic to middle relays, but may also run a pluggable transport (referred to as ``transport'' for shorthand). Pluggable transports specify alternative protocols by which Tor Browser may connect to the Tor network, thereby disguising Tor traffic to make it harder to detect and block bridges. For convenience, bridges are grouped by which transport they run.

@@

Most bridges can be blocked by blocking their static IP addresses. These include bridges that run ``fte'' and ``fte-ipv6''~\cite{fte} pluggable transports, which disguise the Tor protocol as another protocol (such as HTTP); these also include the ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise. Other bridges are less susceptible to blocking because of how they work. Bridges that run the ``flashproxy''~\cite{flashproxy} and ``meek''~\cite{fifield2015blocking} transports route traffic through third party web browsers and content delivery networks. The bridges that are accessible in each country vary. Figure~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of our study.

@@

\subsection{Connecting to Tor} 
It is important to note that there are many valid configuration settings that can be used to connect to the Tor network. A user who does not need a bridge or proxy can still connect with a bridge, proxy, or both, provided that they are configured correctly (though adding unnecessary network hops or obfuscation protocols may slow the connection down).

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F). ``Connect'' starts a connection. ``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}). }
	\label{fig:old-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first bridge screen (B1). ``Yes'' leads to a bridge configuration screen (Figure~\ref{fig:old-bridge-settings}) and ``no'' skips it.}
	\label{fig:old-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The second bridge screen (B2). Users select a bridge here. ``Help'' directs to bridge help screen (Figure~\ref{fig:old-bridge-help}). }
	\label{fig:old-bridge-settings}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{Some hardcoded bridges are listed alphabetically by their transport. The recommended one is obfs3.}
	\label{fig:old-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH) talks about getting a custom bridge. ``Done'' leads back to the previous screen.}
	\label{fig:old-bridge-help}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy question screen (P1). ``Yes'' goes to the proxy settings screen (Figure~\ref{fig:old-proxy-yes}). and ``no'' starts a connection.}
	\label{fig:old-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy settings screen (P2). ``Connect'' starts a connection to Tor with the interface settings.}
	\label{fig:old-proxy-yes}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. }
	\label{fig:old-progress}
\end{subfigure}
\caption{
The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:old-interface}
\end{figure*}

@@

\subsection{Testing Pipeline} 
We performed a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons. A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement. We then conducted qualitative and quantitative usability tests. We believe both methods were necessary for a complete usability evaluation. Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable. We used our observations from the qualitative study to design interface changes that would address common issues that these participants encountered. We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original Tor Launcher interface.

>>>>

Bridges are unlisted alternative entry nodes used to connect to Tor when Tor relays are censored.
Bridges also receive packets from the user and forward traffic to middle relays, but may also run a pluggable transport (referred to as ``transport'' for shorthand). Pluggable transports specify alternative protocols by which Tor Browser may connect to the Tor network, thereby disguising Tor traffic to make it harder to detect and block bridges.
When a bridge is used, it takes the place of the guard relay.
For convenience, bridges are grouped by which transport they run.

@@

Most bridges can be blocked by blocking their static IP addresses. These include bridges that run the ``fte'' and ``fte-ipv6''~\cite{fte} pluggable transports, which disguise the Tor protocol as another protocol (such as HTTP); these also include the ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise. Other bridges are less susceptible to blocking because of how they work. Bridges that run the ``flashproxy''~\cite{flashproxy} and ``meek''~\cite{fifield2015blocking} transports route traffic through third party web browsers and content delivery networks. The bridges and transports that are accessible in each country vary. Figure~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of our study.

@@

\subsection{Connecting to Tor} 
It is important to note that there are many valid configuration settings that can be used to connect to the Tor network. A user may or may not need a combination of proxy and bridge.
A user who does not need a bridge or proxy can still connect with a bridge, proxy, or both, provided that they are configured correctly (though adding unnecessary network hops or obfuscation protocols may slow the connection down).

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F). ``Connect'' starts a connection. ``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}). }
	\label{fig:old-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first bridge screen (B1). ``Yes'' leads to a bridge configuration screen (Figure~\ref{fig:old-bridge-settings}) and ``no'' skips to P1.}
	\label{fig:old-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The second bridge screen (B2). Users select a bridge here. ``Help'' directs to bridge help screen (Figure~\ref{fig:old-bridge-help}). }
	\label{fig:old-bridge-settings}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{Some hardcoded bridges are listed alphabetically by their transport. The recommended one is obfs3.}
	\label{fig:old-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH) talks about getting a custom bridge. ``Done'' leads back to the previous screen.}
	\label{fig:old-bridge-help}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy question screen (P1). ``Yes'' goes to the proxy settings screen (Figure~\ref{fig:old-proxy-yes}). and ``no'' starts a connection.}
	\label{fig:old-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy settings screen (P2). ``Connect'' starts a connection to Tor with the interface settings.}
	\label{fig:old-proxy-yes}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. }
	\label{fig:old-progress}
\end{subfigure}
\caption{
The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:old-interface}
\end{figure*}

@@

\subsection{Testing Pipeline} 
We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons. A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement. We then conducted qualitative and quantitative usability tests. We believe both methods were necessary for a complete usability evaluation. Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable. We used our observations from the qualitative study to design interface changes that would address common issues that these participants encountered. We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original Tor Launcher interface.
